Ground state energy of quantum dots using the coupled cluster method

### 2018-06-07 project_2/article/article.tex
More on HO -> HF conversion

            The neatest, yet arguably the most abstract, way to write the Hartree-Fock
            equations for electron $i$\footnote{This is weird, as electron
            should be indistinguishable and therefor impossible to label.} is
            \begin{equation}
                f_i \varphi_i = \varepsilon_i \varphi_i,
            \end{equation}
            where $f_i$ is the Fock operator, $\varphi_i$ are eigenstates of the Fock
            operator consiting of a set of one-electorn wave funcitons, called the
            Hartree-Fock molecular orbitals, and $\varepsilon_i$ are the eigenenergies
            of the Fock operator. The fock operator, in matrix notation, is given by
            \begin{equation}
                F_{pa} = H_{pq} +  J(D)_{pq} - \frac{1}{2}K(D)_{pq},
            \end{equation}
            where $h_i$ is the one-body operatore, while the two-body operator is
            divided into what we call a direct part,
            \begin{equation}
                J(D)_{pq} = \braket{pq}{rs}D_{sr},
            \end{equation}
            and an exchange part,
            \begin{equation}
                K(D)_{pq} = \braket{ps}{rq}D_{sr}.
            \end{equation}
            The direct part of the two-body operator is comparable to classical Coloumb
            repulsion, while the exchange does not have a classical analog as it arises
            from the antisymmetry requirement of the wavefunction. $D_{sr}$ is the
            density matrix of the system.

@@

>>>>

            The neatest, yet arguably the most abstract, way to write the Hartree-Fock
            equations for electron $i$\footnote{This is weird, as electron
            should be indistinguishable and therefore impossible to label.} is
            \begin{equation}
                f_i \varphi_i = \varepsilon_i \varphi_i,
            \end{equation}
            where $f_i$ is the Fock operator, $\varphi_i$ are eigenstates of the Fock
            operator consiting of a set of one-electorn wave funcitons, called the
            Hartree-Fock molecular orbitals, and $\varepsilon_i$ are the eigenenergies
            of the Fock operator. The fock operator, in matrix notation, is given by
            \begin{equation}
                F_{pa} = H_{pq} +  J(D)_{pq} - \frac{1}{2}K(D)_{pq},
            \end{equation}
            where $h_i$ is the one-body operatore, while the two-body operator is
            divided into what we call a direct part,
            \begin{equation}
                J(D)_{pq} = \braket{pq}{rs}D_{sr},
            \end{equation}
            and an exchange part,
            \begin{equation}
                K(D)_{pq} = \braket{ps}{rq}D_{sr}.
            \end{equation}
            The direct part of the two-body operator is comparable to classical Coloumb
            repulsion, while the exchange does not have a classical analog as it arises
            from the antisymmetry requirement of the wavefunction. $D_{sr}$ is the
            density matrix of the system.

@@

            Because the Hartree-Fock method is a variational method, the initial
            wavefunction made up of the single-partrice wavefunctions $\varphi_i$
            is varied until the minimal energy is found. The transformations necessary
            to make all these variations will now be contained in $C$. So if we start from
            a Harmonic Oscillator (HO) basis we can transform into a better basis, called the
            Hartree-Fock (HF) basis,
            \begin{equation}
                \ket{\Psi}^{\text{HF}}_p = \sum_{k=1}^L C_{kp} \ket{\Psi}_k^{\text{HO}}.
            \end{equation}
            We will see how the coupled cluster method with double excitations works with
            both the HO basis and the HF basis.
